Title

### 2024-06-09 paper/main.tex
Updates

\section{Using measure of association for modifying DAGs}
The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement.

@@

\section{Empirical Analysis}
To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some empirical
analysis.

>>>>

\section{Using measure of association for modifying DAGs}
The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement. Give some examples here.

@@

\section{Empirical Analysis}

To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some empirical
analysis.
